### 2015-09-10 manuscript.Rnw
add LaTeX formatting for sections

Demonstration (1) getting relationships from a list of taxa

Demonstration (2) getting tree from a given study

@@

Demonstration (3) exploring the taxonomy

Demonstration (4) how does rotl fit into the R package ecosystem?

Conclusion

@@

Availability

`rotl` is available both from the CRAN repository
(https://cran.r-project.org/package=rotl) and from GitHub
(https://github.com/ropensci/rotl).

Acknowledgements

>>>>

\section{Demonstrations}
\label{sec:demonstrations}

\subsection{Getting relationships from a list of taxa}
\label{sec:get-relationships}

\subsection{Getting tree from a given study}
\label{sec:get-tree-study}

@@

\subsection{Exploring the taxonomy}
\label{sec:exploring-taxonomy}

\subsection{How does rotl fit into the R package ecosystem?}
\label{sec:how-does-rotl-fit}

\section{Conclusion}
\label{sec:conclusion}

@@

\section{Availability}
\label{sec:availability}

\code{rotl} is available both from the CRAN repository
(https://cran.r-project.org/package=rotl) and from GitHub
(https://github.com/ropensci/rotl).

\section{Acknowledgments}
\label{sec:acknowledgments}
